---
title: "Data visulaization gdx: tryal"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

## 0. Settings

```{r, warning=FALSE, message=FALSE}
#setwd("C:/Users/modin/Desktop/Ettore/UNIVERSITA/ECC_GAMS/R STUDIO")
rm( list = ls() )

list.files()
graphics.off() # chiude tutti i device grafici
cat("\014") #pulisci console

library(tidyverse)
library(gdxtools)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggrepel)
library(ggsci) # scientific colors
library(viridis) #looks good and includes many options
library(RColorBrewer) # wide choice
library(countrycode) # Country name tools

```

# Extract and combine data from different gdx
```{r}
path <- "../../Ecc-Project2/results"


files <- list.files(path,pattern = ".gdx")
myfiles <- file.path(path, files)
myfiles = myfiles %>% str_subset(pattern = "results.*\\.gdx")


myfiles

gdx_bau = list.files(path,pattern = "bau")
gdx_NZ = list.files(path,pattern = "NZ.gdx")
gdx_TCB = list.files(path,pattern = "TCB.gdx")
gdx_NZ_ssp = list.files(path,pattern = "NZ_tfpscen")
gdx_BPU_ssp = list.files(path,pattern = "BPU_tfpscen")

myfiles = c(gdx_NZ,gdx_bau,gdx_TCB)
for ( i in 1:length(myfiles)){
  myfiles[i] = paste0( "../../Ecc-Project2/results/",myfiles[i])
}

myfiles
# TIME
tstep = 5
first_year = 2000
max_year = 2100
```

I_EN
(trad_cars, hybrid, plg_hybrid, edv; elwindon, elwindoff, elpv; ???)

Q_EN
trad_cars, hybrid, plg_hybrid, edv; elwindon, elwindoff, elpv; ???)

MCOST_INV, K_EN
trad_cars, hybrid, plg_hybrid, edv; elwindon, elwindoff, elpv;


Q_FUEL, COST_FUEL,MCOST_FUEL
trbiofuel; advbiofuel; ?
I_OUT: oil, Q_EMI_OUT, Q_OUT, Q_EMI_OUT,Q_OUT
I_RD: battery, K_RD
Q_IN
(trad_cars, hybrid, plg_hybrid, edv; elwindon, elwindoff, elpv; ???)



# VAR CHOICE

```{r}
vars = c("I_EN", "Q_EN", "MCOST_INV", "K_EN","Q_EMI", "BAU_Q_EMI", 
         "W_EMI","Q_FUEL", "COST_FUEL","MCOST_FUEL","I_OUT", "Q_EMI_OUT", #7
         "Q_OUT","Q_OUT","I_RD","TEMP","wcum","battery_cost_new") #13
othervars = c("I_EN_GRID", "K_EN_GRID", "battery_cost_new", "co2_transport", "tpes")

vars2 = c("Q_IN","WCUM_EMI","W_E","QEL_OUT","FPRICE","battery_cost", "battery_cost_new",
          "emi_bio_harv","I_RD","K_RD","UTILITY")

variable = "K_EN"
results <- batch_extract(variable, files = myfiles) 
results = results[[variable]] # move from list to dataframe
results

```

# group 
```{r}
res = results

colnames(res)[1] = "V1"
unique(res$V1)

var_chosen1 = c("edv","plg_hybrid","trad_cars","hybrid")
var_chosen1 = c("battery")
var_chosen1 = c("oil","trbiofuel","advbiofuel")
var_chosen1 = c("co2")
var_chosen1 = c("atm")
res = res[which(res$V1 %in% var_chosen1 ),]
res

chosen_countrys = c("usa")
res = res[which( res$n %in% chosen_countrys),]

colnames(res)[2] = "V2"
var_chosen2 = c("edv","plg_hybrid","trad_cars","hybrid")
res = res[which(res$V2 %in% var_chosen1 ),]

res <- res %>%
group_by(gdx,t) %>%
summarise(value = sum(value))
res

res <- res %>%
group_by(gdx,t,V1) %>%
#summarise(value = sum(value))
summarise(value = mean(value))
res

res <- res %>%
group_by(gdx,t,V1,V2) %>%
summarise(value = sum(value))
#summarise(value = mean(value))
res



unique(res$gdx)
```
# perc diff
```{r}
base = 1
new = 3
paste0(round((1-res$value[base]/res$value[new])*100,2),"%")
```
# data-diff
```{r}
gdxs = unique(res$gdx)
data_diff = res[res$gdx==gdxs[2],"value"]-res[res$gdx==gdxs[1],"value"]
data_perc = data_diff/res[res$gdx==gdxs[1],"value"]
plot(data_diff,type="b",pch=16)
plot(data_perc,type="b",pch=16)
```


# last data transform
```{r}
data = res %>% as_tibble()

data <- data %>%
# Transform time period into year, t0 and tsep could be different
  mutate(year = as.numeric(t) * tstep + first_year) %>% 
  # Transform the filename into a scenario name
  mutate(scen = basename(gdx)) %>% 
  mutate(scen = str_replace(scen, ".gdx", "")) %>%
  mutate(scen = str_replace(scen, "results_", ""))

levs = unique(data$scen)
levs2 = unique(data$V1)

data <- data %>% mutate(scen = factor(scen, levels = levs))
data <- data %>% mutate(V1 = factor(V1, levels = levs2))
data$scen

data
```
# piechart
```{r}
library(RColorBrewer)
myPalette <- brewer.pal(5, "Set2") 

data_time = data[which(data$t==8),]

piechart = ggplot(data_time, aes(x=" ", y=value, fill=V1)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y", start=0)+
  facet_wrap(~scen, ncol = 2)+
    labs(x = " ",  title = "Veichle Fleet CM-usa-2040") 
piechart
```
#save plot
```{r}
ggsave(filename = "Veichle Fleet-USA-cm-2040.png", plot = piechart, width = 15, height = 10, units = "cm") # A4 format
```

#areaplot
```{r}
areaplot = ggplot(data, aes(x=year, y=value, fill=V1)) + 
    geom_area()+
  facet_wrap(~scen, ncol = 3, scales='fixed') +
scale_x_continuous(limits=c(first_year+tstep, max_year),
                    breaks=seq(first_year+tstep, max_year,by = 15)) +
  labs(x = "", y = "TWh", title = paste0(variable,"-world")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
areaplot
  
```

#save plot
```{r}
ggsave(filename = "Q_FUEL-world.png", plot = areaplot, width = 15, height = 10, units = "cm") # A4 format
```
# MAIN PLOTTER
```{r}
plot = ggplot(data %>% filter(year <= max_year),
      aes(x = year, y = value, color = scen)) +
  
#lot = ggplot(data %>% filter(year <= max_year),
#      aes(x = year, y = value, color = V1)) +
  
geom_line(size=1.2) +

#facet_wrap(~scen, ncol = 2, scales='free') +
  
#geom_point() + # NEW GEOMETRY, SAME DATA AND MAPPING

geom_vline(xintercept = 2050, color = 'Black', size = 0.4) +
  
labs(x = "", y = "°C", title = paste0(variable," increase respect to pre-industrial levels")) +
  
theme_bw() +
theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  
scale_x_continuous(limits=c(first_year+tstep, max_year),
                    breaks=seq(first_year+tstep, max_year,by = 10)) +
  
#scale_y_continuous(limits=c(-5, 50)) +
  
#scale_color_discrete(name = "Scenario")
scale_color_viridis(name = "Scenario",discrete = TRUE, option = "H")
plot
```
#save plot
```{r}
ggsave(filename = "TEMP.png", plot = plot, width = 15, height = 10, units = "cm") # A4 format
```


# area between curves
```{r}
v = variable # rename for semplicity

data = res %>% as_tibble()
data <- data %>%
mutate(scen = basename(gdx)) %>% 
mutate(scen = str_replace(scen, ".gdx", "")) %>%
mutate(scen = str_replace(scen, "results_", ""))
levs = unique(data$scen)
data <- data %>% mutate(scen = factor(scen, levels = levs))

scenarios_chosen = c("BPU_TCB_CMBnperc_incr_7","BPU_TCB_CMBnperc_incr_50")

y_up <- data[data$scen==scenarios_chosen[1],]$value  
y_low <- data[data$scen==scenarios_chosen[2],]$value
x <- seq(2005,2150,by=5)
df_combined <- data.frame(x, y_up, y_low)

# Create the plot
plot_curve_region = ggplot() +
  geom_ribbon(data = df_combined, aes(x = x, ymin = y_low, ymax = y_up), 
              fill = "blue", alpha = 0.3) +
  geom_line(data = df_combined, aes(x = x, y = y_up), color = "red",size=1.5) +
  geom_line(data = df_combined, aes(x = x, y = y_low), color = "green",size=1.5) +
  geom_point() + # NEW GEOMETRY, SAME DATA AND MAPPING
  labs(x = "", y = "2005 US$/kWh", title = v) +
  #theme_bw() +
  #theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_x_continuous(limits=c(2010+tstep, 2055),
                    breaks=seq(2010+tstep, 2055,by = 10)) +
  scale_color_manual(values = c("red", "green"), labels = scenarios_chosen) +
  theme(legend.position = "right")+
  theme_bw()

```
# save plot
```{r}

ggsave(filename ="critical material increase.png", plot = plot_curve_region, width = 15, height = 10, units = "cm") # A4 format
```


# world visual-battery_cost
```{r}
# import the WITCH model regional definition
wreg <- read_csv('mapwitch17.csv')
# transforms ISO codes into country names
wreg <- wreg %>% mutate(region = countrycode(ISO, origin = 'iso3c', destination = 'country.name'))
# Correcting some mismatches
#wreg[ISO ='GBR']$region = 'UK'
#wreg[ISO ='USA']$region = 'USA'
wreg

world <- ne_countries(scale = "small", returnclass = "sf")
world <- subset(world,!adm0_a3 %in% c("ATA","FJI"))
# merge the WITCH regional definition with the world map
world <- merge(world,wreg, by.x = "adm0_a3", by.y = "ISO")



# merge with the emission data.frame
world0 <- merge(world,res %>% filter(t == 30), by = "n", allow.cartesian=TRUE)
world1 <- st_transform(world0, crs = target_crs)

# Use a better projection 'equal projection'
target_crs <- '+proj=eqearth +wktext'
my_palette <- c("red", "green")

# Create a new variable indicating whether value is higher than 700
world1$color_category <- ifelse(world1$value > 700, "In posess of rare material", "No rare materials")


```

# other
```{r}

# Plot the map with discrete colors
ggplot(data = world1) +
  geom_sf(aes(fill = color_category)) +
  coord_sf(datum = target_crs, expand = FALSE, clip = "off") +
  scale_fill_manual(name = "Battery Cost",
                    values = setNames(my_palette, c("In posess of rare material", "No rare materials")),
                    guide = guide_legend(title = "Battery Cost")) +
  theme_void()
```





